Hyperopt-Sklearn: Subtitle?

### 2014-04-26 papers/2014-automl/paper.tex
updating numbers after LinearSVC removed

In total, our parameterization had 65 hyperparameters: 6 for preprocessing and 53 for classification.
The search space includes 15 boolean variables, 14 categorical, 17 discrete, and 19 real-valued variables.
Although the total number of hyperparameters is large, the number of {\em active} hyperparameters describing any one model is much smaller: a model consisting of \texttt{PCA} and a \texttt{RandomForest} for example,
would have only 12 active hyperparameters (1 for the choice of preprocessing, 2 internal to PCA, 1 for the choice of classifier and 8 internal to the RF).
Hyperopt description language allows us to differentiate between {\em conditional} hyperparameters (which must always be assigned) and {\em non-conditional} hyperparameters (which may remain unassigned when they would be unused).
We make use of this mechanism extensively so that Hyperopt's search algorithms do not waste time learning by trial and error that e.g. RF hyperparameters have no effect on SVM performance.
Even internally within classifiers, there are instances of conditional parameters: \texttt{KNN} has conditional parameters depending on the distance metric,
and \texttt{LinearSVC} has 3 binary parameters (``loss'', ``penalty'', and ``dual'') that admit only 4 valid joint assignments.
We also included a blacklist of (preprocessing, classifier) pairs that did not work together, e.g. PCA and MinMaxScaler were incompatible with MultinomialNB, TF-IDF could only be used for text data, and the tree-based classifiers were not
compatible with the sparse features produced by the TF-IDF preprocessor.
Allowing for a 10-way discretization of real-valued hyperparameters, and taking these conditional hyperparameters into account, a grid search of our search space would still require an infeasible number of evalutions (on the order of $10^{12}$).

>>>>

In total, our parameterization had 59 hyperparameters: 6 for preprocessing and 53 for classification.
The search space includes 13 boolean variables, 11 categorical, 17 discrete, and 18 real-valued variables.
Although the total number of hyperparameters is large, the number of {\em active} hyperparameters describing any one model is much smaller: a model consisting of \texttt{PCA} and a \texttt{RandomForest} for example,
would have only 12 active hyperparameters (1 for the choice of preprocessing, 2 internal to PCA, 1 for the choice of classifier and 8 internal to the RF).
Hyperopt description language allows us to differentiate between {\em conditional} hyperparameters (which must always be assigned) and {\em non-conditional} hyperparameters (which may remain unassigned when they would be unused).
We make use of this mechanism extensively so that Hyperopt's search algorithms do not waste time learning by trial and error that e.g. RF hyperparameters have no effect on SVM performance.
Even internally within classifiers, there are instances of conditional parameters: \texttt{KNN} has conditional parameters depending on the distance metric,
and \texttt{LinearSVC} has 3 binary parameters (``loss'', ``penalty'', and ``dual'') that admit only 4 valid joint assignments.
We also included a blacklist of (preprocessing, classifier) pairs that did not work together, e.g. PCA and MinMaxScaler were incompatible with MultinomialNB, TF-IDF could only be used for text data, and the tree-based classifiers were not
compatible with the sparse features produced by the TF-IDF preprocessor.
Allowing for a 10-way discretization of real-valued hyperparameters, and taking these conditional hyperparameters into account, a grid search of our search space would still require an infeasible number of evalutions (on the order of $10^{12}$).
